Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-09-07 bbbq_article.tex
Use results from 'bbbq_1_fast'
Use all BBBQ2 figures

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_1/fig_f_tmh_mhc1.png}
  \caption{
    Percentage of MHC-I epitopes overlapping with TMHs
    for a human, viral and bacterial proteome.
  }
  \label{fig:1}
\end{figure}

@@

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_1/fig_f_tmh_mhc2.png}
  \caption{
    \% epitopes overlapping with transmembrane helix
    for a human, COVID-19 and Mycobacterium proteome.
  }
  \label{fig:2}
\end{figure}

@@

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_2/scores_boxplot.png}
  \caption{
    Evolutionary conservation
  }
  \label{fig:evolutionary_conservation_boxplot}
\end{figure}

>>>>

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_1_fast/fig_f_tmh_mhc1_grid.png}
  \caption{
    Percentage of MHC-I epitopes overlapping with TMHs
    for a human, viral and bacterial proteome.
  }
  \label{fig:1}
\end{figure}

@@

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_1_fast/fig_f_tmh_mhc2_grid.png}
  \caption{
    \% epitopes overlapping with transmembrane helix
    for a human, COVID-19 and Mycobacterium proteome.
  }
  \label{fig:2}
\end{figure}

@@

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_2/scores.png}
  \caption{
    Conservation scores across the SARS-CoV-2 proteome
    for proteins that have at least one TMH
  }
  \label{fig:evolutionary_conservation}
\end{figure}

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_2/scores_boxplot.png}
  \caption{
    Evolutionary conservation scores of TMH versus non-TMH
    residues in the SARS-CoV-2 proteome,
    for proteins that have at least one TMH
  }
  \label{fig:evolutionary_conservation_boxplot}
\end{figure}

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_2/scores_all.png}
  \caption{
    Conservation scores across the SARS-CoV-2 proteome
    for all proteins
  }
  \label{fig:evolutionary_conservation}
\end{figure}

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_2/scores_boxplot_all.png}
  \caption{
    Evolutionary conservation scores of TMH versus non-TMH
    residues in the SARS-CoV-2 proteome,
    for all proteins
  }
  \label{fig:evolutionary_conservation_boxplot}
\end{figure}
